\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/appendix.tex
feat: add React text (#86)
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>
Co-authored-by: Adrian Mirza <adrianmirza81@gmail.com>

\begin{table}
    \caption{\textbf{Performance of the models on the \chembench corpus.} The table shows the fraction of questions answered correctly by the models for different skills and difficulty levels.}
    \resizebox{\textwidth}{!}{
    \variable{output/performance_table.tex}
    }
    \label{tab:performance_table}
\end{table}

@@

>>>>

\begin{table}
    \caption{\textbf{Performance of the models on the \chembench corpus.} The table shows the fraction of questions answered correctly by the models for different skills and difficulty levels. Models with \enquote{T-one} in the name were run for a temperature of 1, which allows us to study the temperature effect in the benchmark. Systems with \enquote{ReAct} in the name are tool augmented, i.e., they can call external tools such as web search or a calculator to answer the questions better. However, we limit those systems to ten calls to the \gls{llm}. This constraint often led the systems to not find the correct answer within the specified number of calls. In this case, we consider the answer as incorrect (see \Cref{sec:react-environment}).}
    \resizebox{\textwidth}{!}{
    \variable{output/performance_table.tex}
    }
    \label{tab:performance_table}
\end{table}

@@

\clearpage
\subsection{Tool augmented models} \label{sec:react-environment}
In addition to directly prompting \glspl{llm}, we also investigated the performance of tool-augmented systems.
For this, we investigated the two models which showed the best overall results, \GPTFourO and \ClaudeThreeFiveSonnet (\oone overperformed both models but is not recommended using this model with such \enquote{reasoning} prompts such as ReAct\autocite{yao2022react} or \gls{cot}\autocite{wei2023cot}). 
For both models, we created a ReAct-style tool augmentation environment in which models had access to WolframAlpha, the ArXiv \gls{api}, Wikipedia, and web search (using Brave search \gls{api}).
We based the selection of these tools on the most used tools by humans (see \Cref{fig:tool_use}).
Additionally, we added two specific tools to convert \gls{iupac} names to \gls{smiles}, and \gls{smiles} to \gls{iupac} names.
These conversion tools allow us to better understand how the agents perform for some specific questions in this agent environment configuration.
We implemented the systems using Langchain\autocite{Chase_LangChain_2022} with the default ReAct prompt and constrained the system to a maximum of ten \gls{llm} calls.

While for \ClaudeThreeFiveSonnet the overall performance did not change, we observe a decrease in performance for \GPTFourO compared with the \llm without tools (\Cref{tab:performance_table}). 
If we study the results by each type of question, we observe an improvement for questions regarding electron counts or point groups of compounds.
However, the scores decreased for questions asking about the number of isomers or \gls{ghs} pictograms.
For the specific questions about converting \gls{iupac} names to \gls{smiles}, the results decreased notably despite the models having access to specific tools prepared for those questions. 
By studying the reasoning path for these cases, we found that the error results from the models responding in a format that the LangChain framework with the default ReAct loop cannot handle. 
This indicates that agent frameworks need optimization to be more robust. It involves not only equipping the \glspl{llm} with tools but also necessitates engineering efforts to create robust systems.
